What is web scraping?
1. Web scraping is the common name for extracting data from the Internet. This can include, copy-and-pasting, making ‘calls’ to an API or capturing and parsing the data. (API is the acronym for Application Programming Interface, which is a software intermediary that allows two applications to talk to each other. Each time you use an app like Facebook, send an instant message, or check the weather on your phone, you're using an API.)
2. To master web scraping you must familiarize yourself with HTTP (Hypertext Transfer Protocol) and Internet languages like HTML (Hypertext Markup Language)

We are scraping the data of the Top Scorers of the English Premier League for the season 2018/19.

## Basic Web Scraping
To web scrape we just capture the HTML
```{r}

#rm() is basically 'remove{base}', it is used to Remove Objects from a Specified Environment. list=ls() is base in this command that means you are referring to all the objects present in the workspace. similarly, rm() is used to remove all the objects from the workspace when you use list=ls() as base.
rm(list=ls())

#a new library for making and parsing web pages
library("rvest")

#the web 'call'
url <- "https://www.bbc.com/sport/football/premier-league/top-scorers"

#read the HTML and store it in a variable
webpage <- read_html(url)

```

```{r}

#pulling out names of the players
playernames_data_html <- html_nodes(webpage,'h2.top-player-stats__name.gel-double-pica')

#parsing the nodes
playernames_data <- html_text(playernames_data_html)
head(playernames_data)

```

```{r}

#Let's next grab the names of the teams
teamname_data_html <- html_nodes(webpage,'span.gel-long-primer.team-short-name')
teamname_data <- html_text(teamname_data_html)
head(teamname_data)

```

```{r}

#next we grab the number of goals scored by each player
goals_data_html <- html_nodes(webpage,'span.top-player-stats__goals-scored-number')
goals_data <- html_text(goals_data_html)
head(goals_data)


```

```{r}

#now we are going to take the assists by each player
assists_data_html <- html_nodes(webpage,'span.top-player-stats__assists-number.gel-double-pica')
assists_data <- html_text(assists_data_html)
head(assists_data)


```

```{r}
#next we take total shots taken by a player
ts_data_html <- html_nodes(webpage,'span.percentage-bar-chart__total.gel-pica.shots-total')
ts_data <- html_text(ts_data_html)
head(ts_data)

```

```{r}
#now we take the number of on target shots
ot_data_html <- html_nodes(webpage,'span.percentage-bar-chart__figure.gel-minion.shots-on-goal-total')
ot_data <- html_text(ot_data_html)
head(ot_data)
```

```{r}
#now we take the Percentage of Shots that were on target
pcsog_data_html <- html_nodes(webpage,'span.percentage-bar-chart__percentage.gel-pica.percentage-goals-on-target')
pcsog_data <- html_text(pcsog_data_html)
head(pcsog_data)
```

```{r}

#putting them all together in one dataframe
eplstats_df<-data.frame(Players = playernames_data, Teams = teamname_data, 
                      Goals = goals_data, Assists = assists_data, Total_Shots = ts_data,
                      Shots_On_Target=ot_data, Percentage_Shots_On_Goal=pcsog_data)
View(eplstats_df)

```
